Considering scale in multilayer animal social networks

### 2020-06-18 paper/manuscript.Rmd
fst readd instead of include graphics

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # warning = FALSE,
    # message = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

# source('../scripts/00-variables.R')

library(data.table)
DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lc.png')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

library(data.table)

drake::loadd(vars)

drake::loadd(data)
DT <- sub
setalloccol(DT)

drake::loadd(nobs)

timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
# knitr::include_graphics('../graphics/figure-lc.png')
drake::readd(lc_figure)
```
